\tool: A Multi-Mode BadUSB Device

### 2021-01-06 WOOT/Files/related_work.tex
related work v_2

\section{Related Work}
\label{sec:related_work}

@@

>>>>

\section{Related Work}
\label{sec:related_work}
\hongyi{Move the stuff about USB protocol to Background}\\
\outline{Attack based on USB 1.0, briefly}\\
\outline{Attack based on USB 2.0, focus on works about application and transport layer}\\
\outline{Attack survey table}\\
\outline{Attack or current works about USB Type-C}\\

@@

Since USB 3.1 was introduced with USB Type-C in 2013, display port and HDMI connectors have been provided by USB Type-C, transformation for video streaming data is guaranteed with the other attacks, e.g., protocol masquerading,  protocol corruption and code injection. To our best knowledge, we are the first to combine the host interaction with attack based on USB. Based on USB Type-C, we design Armory, a multi-mode BadUSB device\chaozu{add armory description}

\chaozu{attack table}\\
\chaozu{enum diagram}
